### 2018-04-12 4_input.tex
add grammar to appendix

\begin{figure}[H]
\begin{lstlisting}[mathescape=true,
        caption={Syntax of an input language of \Porthos},
        captionpos=b,
        label={syntax:porthos},
        basicstyle=\ttfamily\footnotesize,
        keywordstyle=\bfseries,
        literate={<--}{$\leftarrow{}$}{1},%{::=}{???},%:\!:\!=},
        morekeywords={if,then,else,return,while,program,thread,mfence,sync,lwsync,isync}]
<prog>  : program <thrd>*
<thrd>  : thread <tid> <inst>
<inst>  : <atom> 
        | <inst> ; <inst>
        | while <pred> <inst>
        | if <pred > then <inst> else <inst>
<atom>  : <reg> <-- <exp> 
        | <reg> <-- <loc>
        | <loc> := <reg> 
        | mfence
        | sync
        | lwsync
        | isync
\end{lstlisting}
%\caption={Syntax of an input language of \Porthos}
%\label={syntax:porthos}
\end{figure}

>>>>

\begin{figure}[H]
\begin{multicols}{2}
\begin{lstlisting}[mathescape=true,
        caption={Syntax of an input language of \Porthos},
        % captionpos=b,
        label={syntax:porthos},
        % basicstyle=\ttfamily\scriptsize,
        % keywordstyle=\bfseries\color{blue},
        %literate={<--}{$\leftarrow{}${}1},%{::=}{???},%:\!:\!=},
        %morekeywords={if,then,else,return,while,program,thread,mfence,sync,lwsync,isync}
        %alsoletter={:,|,;},%
        %morekeywords={:,|,;},%
        %keywordstyle={\color{red}},% 
        breaklines=true,
        % xleftmargin=5mm,framexleftmargin=5mm
        ]
<prog>  : program <thrd>*
<thrd>  : thread <tid> <inst>
<inst>  : <atom> 
    | <inst> ; <inst>
    | while <pred> <inst>
    | if <pred > then <inst> else <inst>
<atom>  : <reg> <-- <exp> 
    | <reg> <-- <loc>
    | <loc> := <reg> 
    | mfence
    | sync
    | lwsync
    | isync
\end{lstlisting}
%\caption={Syntax of an input language of \Porthos}
%\label={syntax:porthos}
\end{multicols}
\end{figure}
